Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-23 WSSSPE1_report/WSSSPE1_summary_report.tex
Response to a remark on use of repositories.

Communities are extremely important in software projects, and both their
building and continued engagement need attention during the project life cycle.
Several of the submitted papers \todo{which ones? should cite here.} discussed how communities have been built around
projects, and what is needed to enable a project to grow. The latter
includes 
public source-code hosting, mailing lists, documentation, wikis, bug trackers, software
downloads, continuous integration, software quality dashboards, and of course,
a general web presence to tie a project's channels and artifacts together.

@@

\section{Case Studies \note{lead: Ketan Maheshwari, contributors: Andy Terrel}} \label{sec:use-cases}

@@

\begin{enumerate}
\item
Successful collaborative projects conducted via the use of shared
repositories are a means towards reproducibility in computational science.
\katznote{this seems rather limited - what else comes out of `successful collaborative projects conducted via the use of shared
repositories'?}

>>>>

Communities are extremely important in software projects, and both their
building and continued engagement need attention during the project life cycle.
Several of the submitted papers \todo{cite} discussed how communities have been built around
projects, and what is needed to enable a project to grow. The latter
includes 
public source-code hosting, mailing lists, documentation, wikis, bug trackers, software
downloads, continuous integration, software quality dashboards, and of course,
a general web presence to tie a project's channels and artifacts together.

@@

\section{Case Studies} \label{sec:use-cases} % \note{lead: Ketan Maheshwari, contributors: Andy Terrel}

@@

\begin{enumerate}
\item Use of shared repositories in the development of collaborative 
projects facilitates collaboration, reproducibility, and sustainability 
in computational science. However it represents a barrier in some scientific fields and 
has yet to be more widely adopted.
